%\acknowledgments

This experiment was sponsored by the Department of Energy Office of Science (DOE), National Science Foundation (NSF), NSERC and the State of Virginia. I am very grateful for the support I received and the opportunities that were available during this time. I am indebted to a seemingly countless number of people for what I have accomplished. I would like to thank the individuals listed below.

My supervisor, Liguang Tang, provided me with many opportunities and I am very grateful for his support through the entire process. When I first joined Hampton University (HU) graduate program, Dr. Tang welcomed me to his research group and explained all the opportunities I can have. He provided many interesting projects to work on, including the weak charge measurement of proton at Jefferson Lab. He encouraged me to attend several conferences during my time at HU, including those in American Physical Society Atlanta, California and Washington conferences. I feel very proud and fortunate to work with my Jefferson Lab supervisor Dave Mack. It was delight working with him. He helped me to understand the lab environment and equipment in many ways. We discussed different topics of experimental nuclear physics field regularly, which helped me to build my knowledge about the field. He always encouraged me to think about great ideas. His deep knowledge and understanding of the field also helped me to solve problems very quickly. I can not thank Dr. Dipangkar Dutta enough for his encouragement and help in my professional and personal life. My research career started at Mississippi State University (MSU) with Dr. Dutta. He introduced me to the Jefferson Lab (JLab) and allowed me to work in different projects with him as my advisor, including the nuclear transparency of kaons and weak charge measurement of the proton at Jefferson Lab. 

I am grateful to all of the friends and colleagues I have come to know at MSU, HU and at JLab. During the three years stay at MSU I had a wonderful experience with our medium energy physics group. Dr. James Dune along with Dr. Dipangkar Dutta helped me a lot. My colleagues at MSU, Amrendra Narayan, Luwani Ndukum, Adesh Subedi, Jed Leggett and Azmi al Masalha also frequently stretched out their helping hand. Special thanks are extended to Amrendra and Shloka Chandavar for their enormous help and support. They were with me always in my ups and downs. The graduate coordinator of the physics department, David Monts, was the nicest person that I can think of. He was always there with me whenever I needed help. I can't thank enough to my closest friends in the department Saurabh Dayal, Nimisha Srivastava, Markandey Tripathi, Peeyush Sahay, Hazem Abusura, Chandrasiri Ihalawela and Ruiyuan Mu for their support throughout.

During my four years at HU I had a wonderful experience with our nuclear physics group. Michael Kohl, Cynthia Keppel and Dr. Liguang Tang helped me a lot. I would like to thank Monique Howard, Ebony Majeed, and Rashinda Davis for their help in administration . My colleagues in the group, Chunhua Chen, Anusha Liguang, Ozgur Ates, and Debaditya Biswas were with me frequently. 

I spent a significant amount of time during my Ph.D career at Jefferson Lab. There were a number of people who were involved in my work and helped me. My experience with Paul King in the software work was great. He was very kind and helped whenever I needed him. Buddhini Waidyawansa and Rakitha Beminiwattha were very nice and helpful throughout the experiment. Wouter Deconinck and Jeong Han Lee were always helping me. Their hard work and dedication also inspired us. I would also like to thank my friends and colleagues, Don Jones, Manolis, Valery, Marty, Jim Dowd, Juan Cornejo, Wade, Josh Hoskins, John Leacock, John Leckey, Scott, Josh Magee, Jie, Peiqing, Siyuan, and Jean-Francois for their support. 

A special thanks goes to my roommate Jonathan Miller who was been with me through my MS thesis. There aren't words to describe the importance of our friendship. John has been there with me in the best and worst of times.

I am thankful to the members of the $Q^p_{weak}$ collaboration whose tireless efforts made the experiment a success. This includes the following spokespeople; Roger Carlini, Stanley Kowalsk and Shelley Page, and the other outstanding physicists involved in the core collaboration. I thank Dave Mack for his successful leadership of the testing, installation, commissioning and operation throughout. I wish to thank the entire Hall-C scientific and technical staff for their operational support of these experiments. I thank Steve Wood for his expertise with the Hall-C data acquisition system. I would like to thank Brad Sawatzky for his kind help to build several new online softwares. Special thanks to Mark Dalton for his helping hand in my analysis, when it needed most. I wish to recognize the efforts of the target group, and particularly Greg Smith, Silviu Covrig and Dave Meekins, for ensuring the successful operation of one of the most complex target used in Jefferson Lab. I want to thank Dave Gaskell for his outstanding contributions as a coordinator for running the experiment smoothly, including performing the M{\o}ller and arc energy measurements. I thank all the scientists and students who took shifts on the experiment so that it could run continuously.

I also wish to thank the accelerator staff and operators for their tireless and outstanding work delivering the high-energy, high-intensity, high-polarization, 100\% duty-factor, stable CW electron beam to Hall-C. I want to thank accelerator operators I worked with, specially Sarin Philip for his great help during the hardware assemble and testing. I want to thank Scott Higgins for his great work in the control system for beam modulation system. Special thanks to Mike Tiefenback for his brilliant ideas and Jay Benesch for his helping hand in my initial days at Jefferson Lab. Pitt Fransis, Simon Wood and Lee Broeker were very helpful in hardware installation and their valuable thoughts.

Also, I want to thank my committee members who read and provided useful feedback for this dissertation: Liguang Tang, Alberto Accardi, Eric Christy, and Dave Mack.

%\end{flushleft}
