%\vita\index{vita}

\begin{center}
\textbf{Curriculum Vita}\\
\end{center}

\begin{center}
{\fontsize{16}{16}\selectfont\bf Nuruzzaman}
%{\Huge Nuruzzaman} 
\end{center} 


\begin{singlespace}
\noindent
\small 12000 Jefferson Ave, Suite 16, Newport News, VA 23606. (757) 952-6686. \href{mailto:nur@jlab.org}{nur@jlab.org}. \href{http://userweb.jlab.org/~nur}{userweb.jlab.org/$\sim$nur}
%\small 542 Coral Court, Apt \# 2D, Newport News, VA 23606. (757) 952-6686. \href{mailto:nur@jlab.org}{nur@jlab.org}
\begin{center}
\large{\textbf{Education}}
\end{center}
\vspace{-5pt}

\noindent
Ph. D. \hspace{0.10cm} Hampton University, Hampton, VA, USA. \hfill December, 2014 \\
\noindent
M. S. \hspace{0.30cm} Mississippi State University, Mississippi State, MS, USA. \hfill August, 2010 \\
\noindent
M. Sc. \hspace{0.10cm} Indian Institute of Technology Roorkee, Uttarakhand, India. \hfill May, 2007 \\
\noindent
B. Sc. \hspace{0.15cm} University of Kalyani, West Bengal, India. \hfill May, 2005 

\begin{center}
\large{\textbf{Professional Experience}}
\end{center}
\vspace{-5pt}

\noindent
Participated in the $Q^p_{weak}$(E02-020), PVDIS(E08-011), HKS(E05-115), HAPPEX-III(E05-109), d2n(E06-014), SANE(E07-003) and GEp-III(E04-108) experiments at Jefferson Lab, Newport News, VA

\begin{center}
\large{\textbf{Honors and Awards}}
\end{center}
\vspace{-23pt}

\begin{changemargin}{-12pt}{0in} 
\begin{itemize}
\setlength{\itemsep}{-1pt}

	\item Received \href{http://www.jsallc.org/IF/IndexJSTF.html}{Junior Scientist Travel Award} from \href{http://www.jsallc.org/index.html}{Jefferson Science Associates (JSA)} for the following conferences: 
\href{http://indico.cern.ch/conferenceDisplay.py?confId=198153}{International Conference on New Frontiers in Physics (ICNFP) 2013} at  Kolymbari, Crete, Greece;
	\href{http://cipanp2012.triumf.ca/}{Eleventh Conference on the Intersections of Particle and Nuclear Physics (CIPANP) 2012} at St. Petersburg, Florida, USA;
	\href{http://cam2009.smf.mx/}{4th Canada-America-Mexico Graduate Students Physics Conference (CAM) 2009} at Acapulco, Guerrero, Mexico.	

	\item Served as the Chairman for the Particle Physics I session in the 4th Canada- America- Mexico Graduate Students Physics Conference on October 22-24, 2009 at Acapulco, Guerrero, Mexico	
	\item Received Merit-cum-means Scholarship from \href{http://www.iitr.ac.in/}{IIT Roorkee} during M.Sc in 2005.
	\item Cleared entrance exam for  \href{http://gate.iitk.ac.in/jam/}{IIT (JAM)} in 2005 with all India rank 154.
	\item Selected for integrated Ph.D. at \href{http://www.ismdhanbad.ac.in/}{Indian School of Mines (ISM)} in 2005 with all India rank 1.

\end{itemize}
\end{changemargin}




\begin{center}
\large{\textbf{Selected Publications and Presentations}}
\end{center}
\vspace{-12pt}

\begin{changemargin}{-10pt}{0in} 
\begin{enumerate} 
%\setlength{\itemindent}{-10pt}
%\setlength{\parskip}{0pt}
%\setlength{\parsep}{0pt}
\setlength{\itemsep}{-1pt}

	\item I. Korover \textit{et al.} 
	Approaching the nucleon-nucleon short-range repulsive core via the 4He(e,e$^{'}$pN) triple coincidence reaction.
	\href{http://arxiv.org/abs/1401.6138}{\textit{arXiv}:1401.6138}  / To be published.

	\item D. Wang \textit{et al.} 
	New Measurement of Parity Violation in Electron-Quark Scattering.
	\href{http://www.nature.com/nature/journal/v506/n7486/full/nature12964.html}{\textit{Nature} \textbf{506} (2014) 7486, 67-70}.

	\item D. Androic \textit{et al.}
	First Determination of the Weak Charge of the Proton.
	\href{http://prl.aps.org/abstract/PRL/v111/i14/e141803}{\textit{Phys. Rev. Lett.} \textbf{111}, 141803 (2013)}. %/\href{http://arxiv.org/abs/arXiv:1307.5275}{arXiv:1307.5275}

	\item D. Wang \textit{et al.}
	Measurement of the Parity-Violating Asymmetry in Electron-Deuteron Scattering in the Nucleon Resonance Region.
	\href{http://prl.aps.org/abstract/PRL/v111/i8/e082501}{\textit{Phys.Rev.Lett.} \textbf{111} (2013) 082501}. %/ \href{http://arxiv.org/abs/arXiv:1304.7741}{arXiv:1304.7741}
		
	\item X. Qiu \textit{et al.}
	Direct Measurements of the Lifetime of Heavy Hypernuclei.
	\href{http://arxiv.org/abs/1212.1133}{\textit{arXiv}:1212.1133}  / To be published.

	\item S. Abrahamyan \textit{et al.}
	New Measurements of the Transverse Beam Asymmetry for Elastic Electron Scattering from Selected Nuclei.
	\href{http://prl.aps.org/abstract/PRL/v109/i19/e192501}{\textit{Phys.Rev.Lett.} \textbf{109} (2012) 192501}. %/\href{http://arxiv.org/abs/1208.6164}{arXiv:1208.6164}

	\item S. Abrahamyan \textit{et al.}
	Measurement of the Neutron Radius of 208Pb Through Parity-Violation in Electron Scattering.
	\href{http://prl.aps.org/abstract/PRL/v108/i11/e112502}{\textit{Phys.Rev.Lett.} \textbf{108} (2012) 112502}. %/ \href{http://arxiv.org/abs/1201.2568}{arXiv:1201.2568}
	
	\item W. Luo \textit{et al.} 
	Polarization components in $\pi^0$ photoproduction at photon energies up to 5.6 GeV.
	\href{http://prl.aps.org/abstract/PRL/v108/i22/e222004}{\textit{Phys.Rev.Lett.} \textbf{108} (2012) 222004}. %/ \href{http://arxiv.org/abs/1109.4650}{arXiv:1109.4650}.
		
	\item Z. Ahmed \textit{et al.}
	New Precision Limit on the Strange Vector Form Factors of the Proton.
	\href{http://prl.aps.org/abstract/PRL/v108/i10/e102001}{\textit{Phys.Rev.Lett.} \textbf{108} (2012) 102001}. %/ \href{http://arxiv.org/abs/1107.0913}{arXiv:1107.0913}

	\item Nuruzzaman \textit{et al.} 
	Nuclear transparency and effective kaon-nucleon cross section from the $A(e,e^\prime K^{+})$ reaction.
	\href{http://prc.aps.org/abstract/PRC/v84/i1/e015210}{\textit{Phys. Rev. C} \textbf{84}, 015210(2011)}. %/ \href{http://arxiv.org/abs/1103.4120}{arXiv:1103.4120}

	\item M. Meziane \textit{et al.} 
	Search for effects beyond the Born approximation in polarization transfer observables in ep elastic scattering.
	\href{http://prl.aps.org/abstract/PRL/v106/i13/e132501}{\textit{Phys. Rev. Lett.} \textbf{106}, 132501(2011)}. %/ \href{http://arxiv.org/abs/1012.0339}{arXiv:1012.0339}

	\item A. J. R. Puckett \textit{et al.}
	Recoil Polarization Measurements of the Proton Electromagnetic Form Factor Ratio to $Q^2$ = 8.5 GeV$^2$.
	\href{http://prl.aps.org/abstract/PRL/v104/i24/e242301}{\textit{Phys. Rev. Lett.} \textbf{104}, 242301(2010)}. %/ \href{http://arxiv.org/abs/1005.3419}{arXiv:1005.3419}

\end{enumerate}
\end{changemargin}


\end{singlespace}
