% exack.tex Acknowledgments
%
This experiment was sponsored by the Department of Energy Office of Science Grant No.: DE-FG02-07ER41528. I am very grateful for the support I received and the opportunities that were available during this time. I am indebted to seemingly countless people for what I have accomplished and, first of all, I would like to say thank you to all of these people.

My supervisor, Dr. Dipangkar Dutta, provided me with many opportunities and I am deeply grateful for his support through the entire process. When I first joined the Mississippi State University graduate program, Dr. Dutta welcomed me to his research group and explained all the opportunities I can have. He provided many interesting projects to work on, including the nuclear transparency of kaons and weak charge measurement of protons at Jefferson Lab. He encouraged me to attend several conferences during my years at MSU, including those in Mexico, St. Louis, Atlanta, California and Washington APS conferences. He went above and beyond in giving me support and encouragement, particularly during the times before meetings and conferences. He was a spokesperson for the experiment in this thesis and he tirelessly answered many questions which I had about the analysis of the experiment.

During the three years stay at MSU, I had a wonderful experience with our medium energy physics group. Dr. James Dune, along with Dr. Dipangkar Dutta, helped me a lot. My colleagues in the group Amrendra Narayan, Luwani Ndukum, Adesh Subedi, Jed Leggett and Azmi al Masalha also extended their helping hands all the time. Special thanks to Amrendra Narayan for his enormous help and support. He was with me always in my ups and downs.

I can't thank enough to my closest friends in the department, Saurabh Dayal, Nimisha Srivastava, Markandey Tripathi, Peeyush Sahay, Hazem Abusura, Chandrasiri Ihalawela, and Ruiyuan Mu for their support throughout.

Also, I want to thank my committee members who read and provided useful feedback on this thesis: Dipangkar Dutta, James A. Dune and David L. Monts.

A special thanks goes to my roommate, Jonathan Miller, who was been with me through my MS thesis. There are not words to describe the importance of our friendship. John has been there with me in the best and worst of times.

I'd also like to specially thanks my friends in the department, Jarrod Marsh, Katja Schaefer, Charles Vaughan, Krishna Kanth Ayyalasomayajula, Quarat Ul-Ann Ijaz, Xin Li, Jie Shu, Sergey Ilyushkin, Jeong Pil Song, and Laalitha Liyanage for all of their support and friendship over the years and because they have become an extended family for me.

I would like to thank my seniors, Vidhu Tiwari and Amitava Moitra, in the department for their help on so many occasions.